Project Notes

### 2020-04-21 notes/notes.tex
Notes: update 21/04/2020

@@

We also use the same process calculus defined before:

\begin{align*}
P ::&= 0 \mid \mu X. P \mid X \\
&\mid p \rhd \{ l_i: P_i \}_{i \in I} \\
&\mid p \lhd l. P \\
&\mid \texttt{if e then } P \texttt{ else } P\\\\
\mathcal{M} ::&= p :: P \\
&\mid \mathcal{M} \mid \mathcal{M}
\end{align*}

The typing judgement for a multiparty session with respect
to the webservice global type builds upon the \textsc{[MTy]}
rule.

\subsection*{Codegen}
\texttt{codegen :: $\mathcal{M}$ $\times$ Role 
$\to$ $\mathcal{M}$}

\subsubsection*{Main rules}

\begin{align*}
&codegen~(p :: q \lhd l_j. P 
\mid q :: p \rhd \{ l_i: Q_i \}_{i \in I} 
\mid s :: S 
\mid \mathcal{M})~s \\
=~&codegen~(p :: s \lhd l. P 
\mid q :: s \rhd \{l_i: Q_i\}_{i \in I}
\mid s :: p \rhd )\\
&where  \\
\dots
\end{align*}

\subsubsection*{Trivial rules}

\subsection*{Encoding}

\subsection*{Preservation}
Modifying the process through code generation preserves
well-typedness of the session.

\paragraph{To show:} let $G_{WS} = (G, p)$. 
If $\mathcal{M}$ is well-typed with respect to $G_{WS}$,
then \texttt{codegen($\mathcal{M},~p$)} is well-typed
with respect to $\llbracket G_{WS} \rrbracket$

>>>>

\paragraph{20/04/2020}
\begin{itemize}
\item
Prove preservation of wellformedness.
\end{itemize}

@@

We define an encoding $\llbracket \cdot \rrbracket :: G_{WS} \to G$
which replaces client-to-client interactions to be routed via
the server role.

\paragraph{Well-formedness} A global type is well-formed if its
projections exist for all participants. Formally,

\[ \text{wellFormed}(G) \Longleftrightarrow 
\forall p \in \texttt{pt}(G). \exists S. (G \upharpoonright p = S) \]

This naturally extends to $G_{WS} = (G, s)$ as we just require that
the server role is a participant in $G$.

\[ \text{wellFormed}_{WS}(G, s) = \text{wellFormed}(G)
\wedge s \in \texttt{pt}(G) \]

\subsection*{Preservation of well-formedness}

Take $G_{WS} = 
(G, s)$ for some global type $G$ and server role $s$.

\paragraph{Proposition}
If $\text{wellFormed}_{WS}(G_{WS})$, 
then $\text{wellFormed}(\llbracket G_{WS} \rrbracket)$.

\paragraph{Proof}
By induction on structure of $G$.
